---
title: "BANA 277 Final Project Cleaned"
output: html_document
date: "2024-03-18"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Install & Read Packages

```{r}
#install.packages("readr")
#install.packages("vctrs")
#install.packages("dplyr")
#install.packages("igraph")
```


```{r}
library(readr)
library(vctrs)
library(dplyr)
library(igraph)
```


##read dataset files

Dataset can be found at: https://snap.stanford.edu/data/twitch_gamers.html 

```{r}
features <- read_csv("/Users/Ethan/Downloads/twitch_gamers/large_twitch_features.csv")
edges <- read_csv("/Users/Ethan/Downloads/twitch_gamers/large_twitch_edges.csv")
print(features)
print(edges)
```

##Modify Indexes to allow for neighbors code to loop through the dataframes
```{r}
# Add 1 to the numeric_id column in features, so neighbor function can iterate through the dataset
features$numeric_id <- features$numeric_id + 1

# Add 1 to the numeric_id_1 and numeric_id_2 columns in edges, same reason
edges$numeric_id_1 <- edges$numeric_id_1 + 1
edges$numeric_id_2 <- edges$numeric_id_2 + 1
```

##Find the highest degree node in order to subset the data

```{r}
## Create the graph using the limited edges dataframe
g <- graph_from_edgelist(as.matrix(edges[, 1:2]), directed = FALSE)


# Use row names of 'features' as vertex names
vertex_names <- rownames(features)
V(g)$name <- vertex_names

# Calculate the degree of each node
degrees <- degree(g)

# Convert the degrees to a dataframe with node IDs
degrees_df <- data.frame(node_id = names(degrees), degree = degrees)

# Sort the dataframe by degree in descending order
degrees_sorted <- degrees_df[order(-degrees_df$degree), ]

# Print the sorted dataframe
print(degrees_sorted)
```

##Create and visualize the network
```{r}
# Function to perform breadth-first search to limit the number of nodes
bfs_limit_nodes <- function(graph, start_node, max_nodes) {
  visited <- rep(FALSE, vcount(graph))  # Initialize visited status for all nodes
  visited[start_node] <- TRUE           # Mark the start node as visited
  queue <- list(start_node)             # Initialize the queue with the start node
  
  while (length(queue) > 0 && sum(visited) < max_nodes) {
    node <- queue[[1]]                  # Dequeue the first node from the queue
    neighbors <- neighbors(graph, node, mode = "all")  # Get neighbors of the current node
    
    for (neighbor in neighbors) {
      if (!visited[neighbor]) {
        visited[neighbor] <- TRUE      # Mark the neighbor as visited
        queue <- c(queue, neighbor)   # Enqueue the neighbor
      }
    }
    
    queue <- queue[-1]                 # Remove the processed node from the queue
  }
  
  ego_nodes <- which(visited)          # Get the indices of visited nodes
  return(ego_nodes)
}

# Find the vertex corresponding to node 61863
vertex_61863 <- which(V(g)$name == "61863")

# Set the maximum number of nodes in the ego network (adjust as needed)
max_nodes <- 1000

# Extract nodes for the ego network with a maximum number of nodes using BFS
ego_nodes <- bfs_limit_nodes(g, vertex_61863, max_nodes)

# Extract the subgraph containing the ego network
ego_network <- induced_subgraph(g, vids = ego_nodes)

# Plot the ego network
plot(
  ego_network,
  vertex.label = ifelse(V(ego_network)$name == "61863", V(ego_network)$name, NA),
  vertex.label.cex = 1.5
)
```

##Create a network visualization with node size scaled by degree

```{r}
ego_degrees <- degree(ego_network)

# Create a dataframe to store node IDs and their corresponding degrees
ego_degrees_df <- data.frame(node_id = V(ego_network)$name, degree = ego_degrees)

node_61683_index <- which(ego_degrees_df$node_id == "61683")

# Create a vector to store edge colors
edge_colors <- rep("lightgray", length(E(ego_network)))

# Find the edges connected to node 61683
edges_connected_to_node_61683 <- which(ends(ego_network, E(ego_network))[1, ] == node_61683_index |
                                      ends(ego_network, E(ego_network))[2, ] == node_61683_index)

# Assign red color to edges connected to node 61683
edge_colors[edges_connected_to_node_61683] <- "red"

node_size <- 0.05 * sqrt(ego_degrees_df$degree)

# Define edge colors vector (use red for edges connected to node 61863, and black for others)

# Plot the ego network with customized visualization parameters
plot(
  ego_network,
  vertex.size = node_size,
  vertex.label = ifelse(V(ego_network)$name == "61863", V(ego_network)$name, NA),
  vertex.label.cex = 1.5,
  edge.color = edge_colors
)
```

##Eigenvector Centrality Analysis:

```{r}
eigenvector_centrality <- evcent(ego_network)$vector
ego_degrees <- degree(ego_network)

# Create a dataframe to store node IDs and their corresponding degrees
ego_degrees_df <- data.frame(node_id = V(ego_network)$name, degree = ego_degrees)
# Create a dataframe to store node IDs and eigenvector centrality
eigenvector_centrality_df <- data.frame(
  Node = V(ego_network)$name,
  Eigenvector_Centrality = eigenvector_centrality
)

eigenvector_centrality_df <- eigenvector_centrality_df[order(-eigenvector_centrality_df$Eigenvector_Centrality), ]
ego_degrees_df <- ego_degrees_df[order(-ego_degrees_df$degree), ]
# Print the sorted dataframe
print(eigenvector_centrality_df)
print(ego_degrees_df)
```

##Merge degree with features in order to run regression models:

```{r}
df <- merge(features, ego_degrees_df, by.x = "numeric_id", by.y = "node_id")

# Print the merged dataframe
print(df)
```

##Poisson regression:

```{r}
model <- glm(degree ~ views + mature + life_time + affiliate, data = df, family = poisson)

# Print the summary of the model
summary(model)
```

```{r}
model <- glm(views ~ degree + affiliate + mature +life_time, data = df, family = poisson)

# Print the summary of the model
summary(model)
```


##Exploratory Analysis of features

```{r}
affiliate_counts <- table(df$affiliate)

# Print the counts
print(affiliate_counts)
```

```{r}
median(df$views)
mean(df$views)
```

```{r}
mature_counts <- table(df$mature)

# Print the counts
print(mature_counts)
```
```{r}
summary(df$life_time)
max(df$life_time)
```
```{r}
dead_counts <- table(df$dead_account)

# Print the counts
print(dead_counts)
```

##Exploratory Analysis Histograms & Barplot

```{r}
hist(df$mature, main = "Distribution of 'mature'", xlab = "Mature", col = "purple")
hist(df$life_time, main = "Distribution of 'life_time'", xlab = "Life Time", col = "purple")
hist(df$affiliate, main = "Distribution of 'affiliate'", xlab = "Affiliate", col = "purple")
hist(df$views, main = "Distribution of 'views'", xlab = "Views", col = "purple")
hist(df$dead_account, main = "Distribution of 'dead accounts'", xlab = "dead account", col = "purple")


barplot(table(df$language), main = "Distribution of 'language'", 
        xlab = "Language", ylab = "Frequency",
        las = 2, col = "purple")  # Rotate labels vertically
```

